Forecasting the 2024 U.S. Presidential Election: Kamala Harris' Projected Victory

### 2024-11-04 paper/paper.qmd
commmiting changes to paper.qmd

## Model Setup
In this section, we outline the statistical models employed to predict the probabilities of victory for Donald Trump and Kamala Harris in the 2024 presidential election within key battleground states. Our analysis utilizes a Bayesian framework, which allows us to incorporate uncertainty and prior information into the modeling process, yielding more robust predictions. The primary estimand for both models is the probability of each candidate's victory, expressed through a logistic regression approach. By examining polling data and its temporal dynamics, we aim to capture the evolving nature of voter support leading up to the election. We present separate subsections for the models of Donald Trump and Kamala Harris, detailing the structure, variables, and assumptions underlying each model. This division allows for a focused discussion on how each model has been tailored to reflect the unique electoral contexts and polling dynamics for each candidate.

@@

# Additional Data Details {#sec-data-details}

Given the nature of the presidential election, the electoral college is more impactful and influential on the possible outcome compared to the nationwide popular votes. Therefore, the majority of the pollsters choose to focus on the battleground states to perform their polling, to gain more insight into the public sentiment specific to certain states. For instance, Sienna/NYT mentions that they have in-state interviewers who call their respondents in states such as Arizona, Georgia, Michigan, Nevada, Pennsylvania, and Wisconsin.

>>>>

## Model Setup
Our models were ran in R [@citeR] using the 'rstanarm' package of @rstanarm.

@@

# Additional Data Details {#sec-data-details}
Given the nature of the presidential election, the electoral college is more impactful and influential on the possible outcome compared to the nationwide popular votes. Therefore, the majority of the pollsters choose to focus on the battleground states to perform their polling, to gain more insight into the public sentiment specific to certain states. For instance, Sienna/NYT mentions that they have in-state interviewers who call their respondents in states such as Arizona, Georgia, Michigan, Nevada, Pennsylvania, and Wisconsin.
